Constraining galaxy assembly bias with galaxy-galaxy measurements of Sloan Digital Sky Survey

### 2016-02-08 text/ms.tex
updating the text and the list of papers

In galaxy-galaxy lensing, the connection between dark matter and galaxies is probed by measuring 
the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
as the ensemble average of the product of galaxy over densities and matter overdensities
\beq
\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
\eeq
where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
and galaxies.

This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
lenses,
\begin{eqnarray}
\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}}.
\end{eqnarray}

>>>>

In g-g lensing, the connection between dark matter and galaxies is probed by measuring 
the cross correlation between the two. In particular, one can define the galaxy-matter cross correlation 
as the ensemble average of the product of galaxy over densities and matter overdensities
\beq
\xi_{gm}(r) = \langle \delta_{g}(\vec{x}) \delta_{m}(\vec{x}+\vec{r}) \rangle,
\eeq
where $\delta_g$ and $\delta_m$ are overdensities of matter and galaxies respectively and we have 
assumed the cross-corrlation depends only on the radial separation due to isotropy in distribution of matter
and galaxies.

This cross correlation can be related to the azimuthally-averaged  projected surface density of the gravitational
lenses,
\begin{eqnarray}
\Sigma(R) &=& \bar{\rho}_{m}(z)\int_{0}^{\infty} \;  [1 + \xi_{gm}(\sqrt{\chi^2 + R^2})] \; d\chi \nonumber \\
          &=& 2\bar{\rho}_{m}(z)\int_{R}^{\infty} \; [1 + \xi_{gm}(r)] \; \frac{rdr}{\sqrt{r^{2} - R^{2}}},
\end{eqnarray}
where $\chi$ is the projected comoving line-of-sight distance, and $R$ is the projected comoving transverse distance.

Since the galaxy-matter cross correlation falls off rapidly that in practice thre redshoft evolution of $\xi_{gm}$ 
can be neglected, integrating only out to a line-fo-sight distance of $\chi=$ 50 Mpc is sufficient. 
The mean excess projected density $\bar{\Sigma}(R)$ can be approximated by the following radial integral,
\beq
\bar{\Sigma}(R , z_{l}) = 2 \rho_{c,0}\Omega_{m,0}\int_{0}^{\mathrm{50Mpc}} \; \xi_{gm}\Big(\sqrt{R^{2}+\chi^{2}},z_{L} \Big)d\chi.
\eeq
